\begin{bibdiv}
\begin{biblist}

%\bibitem[Lawlor]{lawlor} Lawlor G., \textit{A new Area-Maximization Proof for the Circle,} Math. Intelligencer 20 (1998) no.1.

\bib{rox}{article}{
   title={Geometric group theory, hyperbolic dynamics and symplectic
   geometry},
   note={Abstracts from the workshop held July 15--21, 2012;
   Organized by Gerhard Knieper, Leonid Polterovich and Leonid Potyagailo},
   journal={Oberwolfach Rep.},
   volume={9},
   date={2012},
   number={3},
   pages={2139--2203},
   %issn={1660-8933},
   %review={\MR{3156727}},
   %doi={10.4171/OWR/2012/35},
}


\bib{abresch-gromoll}{article}{
   author={Abresch, Uwe},
   author={Gromoll, Detlef},
   title={On complete manifolds with nonnegative Ricci curvature},
   journal={J. Amer. Math. Soc.},
   volume={3},
   date={1990},
   number={2},
   pages={355--374},
   %issn={0894-0347},
   %review={\MR{1030656 (91a:53071)}},
   %doi={10.2307/1990957},
}

\bib{akopyan-tarasov}{article}{
   author={Akopyan, A. V.},
   author={Tarasov, A. S.},
   title={A constructive proof of Kirszbraun's theorem},
   %language={Russian},
   %journal={Mat. Zametki},
   %volume={84},
   %date={2008},
   %number={5},
   %pages={781--784},
   %issn={0025-567X},
   %translation={
      journal={Math. Notes},
      volume={84},
      date={2008},
      number={5-6},
      pages={725--728},
      %issn={0001-4346},
   %},
   %review={\MR{2500644 (2010c:47123)}},
   %doi={10.1134/S000143460811014X},
}

\bib{alexander-osserman}{article}{
   author={Alexander, H.},
   author={Osserman, R.},
   title={Area bounds for various classes of surfaces},
   journal={Amer. J. Math.},
   volume={97},
   date={1975},
   number={3},
   pages={753--769},
   %issn={0002-9327},
   %review={\MR{0380596 (52 \#1495)}},
}

\bib{alexander-hoffman-osserman}{article}{
   author={Alexander, H.},
   author={Hoffman, D.},
   author={Osserman, R.},
   title={Area estimates for submanifolds of Euclidean space},
   conference={ title={Symposia Mathematica, Vol. XIV},address={Convegno di Teoria Geometrica dell'Integrazione e Variet\`a Minimali, INDAM, Rome},date={1973},},
   book={
      publisher={Academic Press, London},
   },
   date={1974},
   pages={445--455},
   %review={\MR{0388253 (52 \#9090)}},
}

\bib{ralexander}{article}{
   author={Alexander, Ralph},
   title={Lipschitzian mappings and total mean curvature of polyhedral
   surfaces. I},
   journal={Trans. Amer. Math. Soc.},
   volume={288},
   date={1985},
   number={2},
   pages={661--678},
   %issn={0002-9947},
   %review={\MR{776397 (86c:52004)}},
   %doi={10.2307/1999957},
}

\bib{alexander}{article}{
   author={Alexander, S.},
   title={Locally convex hypersurfaces of negatively curved spaces},
   journal={Proc. Amer. Math. Soc.},
   volume={64},
   date={1977},
   number={2},
   pages={321--325},
   %issn={0002-9939},
   %review={\MR{0448262 (56 \#6571)}},
}

\bib{ABB}{article}{
   author={Alexander, Stephanie B.},
   author={Berg, I. David},
   author={Bishop, Richard L.},
   title={Geometric curvature bounds in Riemannian manifolds with boundary},
   journal={Trans. Amer. Math. Soc.},
   volume={339},
   date={1993},
   number={2},
   pages={703--716},
   %issn={0002-9947},
   %review={\MR{1113693 (93m:53034)}},
   %doi={10.2307/2154294},
} 

\bib{akp}{book}{
   author={Alexander, S.},
   author={Kapovitch, V.},
   author={Petrunin A.},
   title={Alexandrov geometry},
   status={in preparation}
}

\bib{alexandrov1948}{book}{
   author={Aleksandrov, A. D.},
   title={Vnutrennyaya Geometriya Vypuklyh Poverhnoste\u\i},
   %language={Russian},
   publisher={OGIZ, Moscow-Leningrad},
   date={1948},
   %pages={387},
   %review={\MR{0029518 (10,619c)}},
}

\bib{alexandrov-finite}{article}{
    Author = {Alexandroff, P.},
    Title = {Diskrete R\"aume.},
    Journal = {Recueil Math\'ematique. Nouvelle S\'erie},
    %Journal = {{Rec. Math. Moscou, n. Ser.}},
    Volume = {2},
    Pages = {501--519},
    Year = {1937},
    Publisher = {Moscow Mathematical Society, Moscow},
    %Language = {German},
    %MSC2010 = {54-XX},
    %Zbl = {0018.09105}
}

\bib{almgren}{article}{
   author={Almgren, F.},
   title={Optimal isoperimetric inequalities},
   journal={Indiana Univ. Math. J.},
   volume={35},
   date={1986},
   number={3},
   pages={451--547},
   %issn={0022-2518},
   %review={\MR{855173 (88c:49032)}},
   %doi={10.1512/iumj.1986.35.35028},
}


\bib{aloff-wallach}{article}{
   author={Aloff, Simon},
   author={Wallach, Nolan R.},
   title={An infinite family of distinct $7$-manifolds admitting positively
   curved Riemannian structures},
   journal={Bull. Amer. Math. Soc.},
   volume={81},
   date={1975},
   pages={93--97},
   %issn={0002-9904},
   %review={\MR{0370624 (51 \#6851)}},
}

\bib{andrews}{article}{
   author={Andrews, Ben},
   title={Contraction of convex hypersurfaces in Riemannian spaces},
   journal={J. Differential Geom.},
   volume={39},
   date={1994},
   number={2},
   pages={407--431},
   %issn={0022-040X},
   %review={\MR{1267897 (95b:53044)}},
}

\bib{antoine}{article}{
   author={Antoine, Louis},
   title={Sur l'homeomorphisme de deux figures et leurs voisinages},
   journal={J. Math. Pures Appl.},
   volume={4},
   date={1921},
   number={},
   pages={221--325},
}

\bib{balacheff-croke-katz}{article}{
   author={Balacheff, Florent},
   author={Croke, Christopher},
   author={Katz, Mikhail G.},
   title={A Zoll counterexample to a geodesic length conjecture},
   journal={Geom. Funct. Anal.},
   volume={19},
   date={2009},
   number={1},
   pages={1--10},
   %issn={1016-443X},
   %review={\MR{2507217 (2010k:53062)}},
   %doi={10.1007/s00039-009-0708-9},
}


\bib{bangert}{article}{
   author={Bangert, Victor},
   title={Geodesics and totally convex sets on surfaces},
   journal={Invent. Math.},
   volume={63},
   date={1981},
   number={3},
   pages={507--517},
   %issn={0020-9910},
   %review={\MR{620682 (82g:53050)}},
   %doi={10.1007/BF01389067},
}

\bib{bazajkin}{article}{
   author={Baza{\u\i}kin, Ya. V.},
   title={On a family of $13$-dimensional closed Riemannian manifolds of
   positive curvature},
   %language={Russian, with Russian summary},
   journal={Sibirsk. Mat. Zh.},
   volume={37},
   date={1996},
   number={6},
   pages={1219--1237, ii},
   issn={0037-4474},
   translation={
      journal={Siberian Math. J.},
      volume={37},
      date={1996},
      number={6},
      %pages={1068--1085},
      %issn={0037-4466},
   },
   %review={\MR{1440379 (98c:53045)}},
   %doi={10.1007/BF02106732},
}

\bib{belk-connelly}{article}{
author={Belk, Maria},
author={Connelly, Robert},
title={Making contractions continuous: 
a problem related to the Kneser--Poulsen conjecture},
eprint={math.bard.edu/~mbelk/}
}

\bib{bennequin}{article}{
   author={Bennequin, Daniel},
   title={Exemples d'immersions du disque dans le plan qui ne sont pas
   projections de plongements dans l'espace},
   %language={French, with English summary},
   journal={C. R. Acad. Sci. Paris S\'er. A-B},
   volume={281},
   date={1975},
   number={2-3},
   pages={Aii, A81--A84},
   %review={\MR{0380806 (52 \#1703)}},
}

\bib{berg}{article}{
   author={Berg, I. D.},
   title={An estimate on the total curvature of a geodesic in Euclidean
   $3$-space-with-boundary},
   journal={Geom. Dedicata},
   volume={13},
   date={1982},
   number={1},
   pages={1--6},
   %issn={0046-5755},
   %review={\MR{679213 (84d:53049)}},
   %doi={10.1007/BF00149423},
}

\bib{besicovitch}{article}{
   author={Besicovitch, A. S.},
   title={On two problems of Loewner},
   journal={J. London Math. Soc.},
   volume={27},
   date={1952},
   pages={141--144},
   %issn={0024-6107},
   %review={\MR{0047126 (13,831d)}},
}

\bib{bezdek-connelly}{article}{
   author={Bezdek, K{\'a}roly},
   author={Connelly, Robert},
   title={Pushing disks apart---the Kneser-Poulsen conjecture in the plane},
   journal={J. Reine Angew. Math.},
   volume={553},
   date={2002},
   pages={221--236},
   %issn={0075-4102},
   %review={\MR{1944813 (2003m:52001)}},
   %doi={10.1515/crll.2002.101},
}

\bib{bing}{article}{
   author={Bing, R. H.},
   title={Some aspects of the topology of $3$-manifolds related to the
   Poincar\'e conjecture},
   conference={
      title={Lectures on modern mathematics, Vol. II},
   },
   book={
      publisher={Wiley, New York},
   },
   date={1964},
   pages={93--128},
   %review={\MR{0172254 (30 \#2474)}},
}

\bib{birkhoff}{article}{
   author={Birkhoff, George D.},
   title={Proof of Poincar\'e's geometric theorem},
   journal={Trans. Amer. Math. Soc.},
   volume={14},
   date={1913},
   number={1},
   pages={14--22},
   %issn={0002-9947},
   %review={\MR{1500933}},
   %doi={10.2307/1988766},
}

\bib{bishop-o'neill}{article}{
   author={Bishop, R. L.},
   author={O'Neill, B.},
   title={Manifolds of negative curvature},
   journal={Trans. Amer. Math. Soc.},
   volume={145},
   date={1969},
   pages={1--49},
   %issn={0002-9947},
   %review={\MR{0251664 (40 \#4891)}},
}

\bib{bochner}{article}{
   author={Bochner, S.},
   title={Vector fields and Ricci curvature},
   journal={Bull. Amer. Math. Soc.},
   volume={52},
   date={1946},
   pages={776--797},
   %issn={0002-9904},
   %review={\MR{0018022 (8,230a)}},
}

\bib{boehm-wilking}{article}{
   author={B{\"o}hm, Christoph},
   author={Wilking, Burkhard},
   title={Manifolds with positive curvature operators are space forms},
   journal={Ann. of Math. (2)},
   volume={167},
   date={2008},
   number={3},
   pages={1079--1097},
   %issn={0003-486X},
   %review={\MR{2415394 (2009h:53146)}},
   %doi={10.4007/annals.2008.167.1079},
}

\bib{bowditch}{article}{
   author={Bowditch, B. H.},
   title={Notes on locally ${\rm CAT}(1)$ spaces},
   conference={
      title={Geometric group theory},
      address={Columbus, OH},
      date={1992},
   },
   book={
      series={Ohio State Univ. Math. Res. Inst. Publ.},
      volume={3},
      publisher={de Gruyter, Berlin},
   },
   date={1995},
   pages={1--48},
   %review={\MR{1355101 (97e:53070)}},
}

\bib{brehm}{article}{
   author={Brehm, Ulrich},
   title={Extensions of distance reducing mappings to piecewise congruent
   mappings on $\mathbb{R}^{m}$},
   journal={J. Geom.},
   volume={16},
   date={1981},
   number={2},
   pages={187--193},
   %issn={0047-2468},
   %review={\MR{642266 (83b:51020)}},
   %doi={10.1007/BF01917587},
}

\bib{brendle-marques-neve}{article}{
   author={Brendle, Simon},
   author={Marques, Fernando C.},
   author={Neves, Andre},
   title={Deformations of the hemisphere that increase scalar curvature},
   journal={Invent. Math.},
   volume={185},
   date={2011},
   number={1},
   pages={175--197},
   %issn={0020-9910},
   %review={\MR{2810799 (2012h:53094)}},
   %doi={10.1007/s00222-010-0305-4},
}

\bib{buser-gromoll}{article}{
   author={Buser, Peter},
   author={Gromoll, Detlef},
   title={On the almost negatively curved $3$-sphere},
   conference={
      title={Geometry and analysis on manifolds},
      address={Katata/Kyoto},
      date={1987},
   },
   book={
      series={Lecture Notes in Math.},
      volume={1339},
      publisher={Springer, Berlin},
   },
   date={1988},
   pages={78--85},
   %review={\MR{961474 (90a:53042)}},
   %doi={10.1007/BFb0083048},
}

\bib{buser-karcher}{book}{
   author={Buser, Peter},
   author={Karcher, Hermann},
   title={Gromov's almost flat manifolds},
   series={Ast\'erisque},
   volume={81},
   publisher={Soci\'et\'e Math\'ematique de France, Paris},
   date={1981},
   pages={148},
   %review={\MR{619537 (83m:53070)}},
}


\bib{bbi}{book}{
   author={Burago, Dmitri},
   author={Burago, Yuri},
   author={Ivanov, Sergei},
   title={A course in metric geometry},
   series={Graduate Studies in Mathematics},
   volume={33},
   publisher={American Mathematical Society, Providence, RI},
   date={2001},
   pages={xiv+415},
   %isbn={0-8218-2129-6},
   %review={\MR{1835418 (2002e:53053)}},
}

\bib{burago-zalgaller}{book}{
   author={Burago, Yu. D.},
   author={Zalgaller, V. A.},
   title={Geometric inequalities},
   series={Grundlehren der Mathematischen Wissenschaften [Fundamental
   Principles of Mathematical Sciences]},
   volume={285},
   %note={Translated from the Russian by A. B. Sosinski\u\i;
   %Springer Series in Soviet Mathematics},
   publisher={Springer-Verlag, Berlin},
   date={1988},
   %pages={xiv+331},
   %isbn={3-540-13615-0},
   %review={\MR{936419 (89b:52020)}},
   %doi={10.1007/978-3-662-07441-1},
}

\bib{BIS}{article}{
   author={Burago, D.},
   author={Ivanov, S.},
   author={Shoenthal, D.},
   title={Two counterexamples in low-dimensional length geometry},
   journal={Algebra i Analiz},
   volume={19},
   date={2007},
   number={1},
   pages={46--59},
   %issn={0234-0852},
   %translation={
      %journal={St. Petersburg Math. J.},
      %volume={19},
      %date={2008},
      %number={1},
      %pages={33--43},
      %issn={1061-0022},
  % },
   %review={\MR{2319509 (2008b:53101)}},
   %doi={10.1090/S1061-0022-07-00984-3},
}

\bib{burago-kleiner}{article}{
   author={Burago, D.},
   author={Kleiner, B.},
   title={Rectifying separated nets},
   journal={Geom. Funct. Anal.},
   volume={12},
   date={2002},
   number={1},
   pages={80--92},
   %issn={1016-443X},
   %review={\MR{1904558 (2003h:26020)}},
   %doi={10.1007/s00039-002-8238-8},
}

\bib{buyalo}{article}{
   author={Buyalo, S. V.},
   title={Volume and fundamental group of a manifold of nonpositive
   curvature},
   %language={Russian},
   journal={Mat. Sb. (N.S.)},
   volume={122(164)},
   date={1983},
   number={2},
   pages={142--156},
   %issn={0368-8666},
   %review={\MR{717671 (86a:53043)}},
}

\bib{zeb}{misc}{    
    title={Is it possible to capture a sphere in a knot?},    
    author={Zarathustra Elessar Brady},    
    note={Question 8091},    
    eprint={http://mathoverflow.net/q/8091},    
    organization={MathOverflow}  
}


\bib{calabi}{article}{
   author={Calabi, Eugenio},
   title={On manifolds with non-negative Ricci curvature II},
   journal={Notices AMS},
   volume={22},
   date={1975},
   pages={A205},
   %issn={0010-1354},
   %review={\MR{758530 (85m:54027)}},
}


\bib{calka}{article}{
   author={Ca{\l}ka, Aleksander},
   title={On conditions under which isometries have bounded orbits},
   journal={Colloq. Math.},
   volume={48},
   date={1984},
   number={2},
   pages={219--227},
   %issn={0010-1354},
   %review={\MR{758530 (85m:54027)}},
}

\bib{cheeger}{article}{
   author={Cheeger, Jeff},
   title={Some examples of manifolds of nonnegative curvature},
   journal={J. Differential Geometry},
   volume={8},
   date={1973},
   pages={623--628},
   %issn={0022-040X},
   %review={\MR{0341334 (49 \#6085)}},
}

\bib{cheeger-colding}{article}{
   author={Cheeger, Jeff},
   author={Colding, Tobias H.},
   title={Lower bounds on Ricci curvature and the almost rigidity of warped
   products},
   journal={Ann. of Math. (2)},
   volume={144},
   date={1996},
   number={1},
   pages={189--237},
   %issn={0003-486X},
   %review={\MR{1405949 (97h:53038)}},
   %doi={10.2307/2118589},
}

\bib{croke-eigenvalue}{article}{
   author={Croke, Christopher B.},
   title={Some isoperimetric inequalities and eigenvalue estimates},
   journal={Ann. Sci. \'Ecole Norm. Sup. (4)},
   volume={13},
   date={1980},
   number={4},
   pages={419--435},
   %issn={0012-9593},
   %review={\MR{608287 (83d:58068)}},
}

\bib{croke-4d}{article}{
   author={Croke, Christopher B.},
   title={A sharp four-dimensional isoperimetric inequality},
   journal={Comment. Math. Helv.},
   volume={59},
   date={1984},
   number={2},
   pages={187--192},
   %issn={0010-2571},
   %review={\MR{749103 (85f:53060)}},
   %doi={10.1007/BF02566344},
}

\bib{croke-energy}{article}{
   author={Croke, Christopher B.},
   title={Lower bounds on the energy of maps},
   journal={Duke Math. J.},
   volume={55},
   date={1987},
   number={4},
   pages={901--908},
   %issn={0012-7094},
   %review={\MR{916127 (88k:58025)}},
   %doi={10.1215/S0012-7094-87-05544-X},
}

\bib{croke}{article}{
   author={Croke, Christopher B.},
   title={Small volume on big $n$-spheres},
   journal={Proc. Amer. Math. Soc.},
   volume={136},
   date={2008},
   number={2},
   pages={715--717 %(electronic)
   },
   %issn={0002-9939},
   %review={\MR{2358513 (2008h:53044)}},
   %doi={10.1090/S0002-9939-07-09079-X},
}

\bib{edelstein-schwatz}{article}{
   author={Edelstein, Michael},
   author={Schwarz, Binyamin},
   title={On the length of linked curves},
   journal={Israel J. Math.},
   volume={23},
   date={1976},
   number={1},
   pages={94--95},
   %issn={0021-2172},
   %review={\MR{0397558 (53 \#1417)}},
}

\bib{efimov}{article}{
   author={Efimov, N. V.},
   title={Qualitative problems of the theory of deformation of surfaces},
   %language={Russian},
   journal={Uspehi Matem. Nauk (N.S.)},
   volume={3},
   date={1948},
   number={2(24)},
   pages={47--158},
   %issn={0042-1316},
   %review={\MR{0027567 (10,324a)}},
}

\bib{EWW}{article}{
   author={Ekholm, Tobias},
   author={White, Brian},
   author={Wienholtz, Daniel},
   title={Embeddedness of minimal surfaces with total boundary curvature at
   most $4\pi$},
   journal={Ann. of Math. (2)},
   volume={155},
   date={2002},
   number={1},
   pages={209--234},
   issn={0003-486X},
   review={\MR{1888799 (2003f:53010)}},
   doi={10.2307/3062155},
}

\bib{eschenburg-spaces}{article}{
   author={Eschenburg, J.-H.},
   title={New examples of manifolds with strictly positive curvature},
   journal={Invent. Math.},
   volume={66},
   date={1982},
   number={3},
   pages={469--480},
   %issn={0020-9910},
   %review={\MR{662603 (83i:53061)}},
   %doi={10.1007/BF01389224},
}

\bib{eschenburg}{article}{
   author={Eschenburg, J.-H.},
   title={Local convexity and nonnegative curvature---Gromov's proof of the
   sphere theorem},
   journal={Invent. Math.},
   volume={84},
   date={1986},
   number={3},
   pages={507--522},
   %issn={0020-9910},
   %review={\MR{837525 (87j:53080)}},
   %doi={10.1007/BF01388744},
}


\bib{falconer}{book}{
   author={Falconer, K. J.},
   title={The geometry of fractal sets},
   series={Cambridge Tracts in Mathematics},
   volume={85},
   publisher={Cambridge University Press, Cambridge},
   date={1986},
   %pages={xiv+162},
   %isbn={0-521-25694-1},
   %isbn={0-521-33705-4},
   %review={\MR{867284 (88d:28001)}},
}

\bib{FMR}{article}{
   author={Fang, Fuquan},
   author={Mendon{\c{c}}a, S{\'e}rgio},
   author={Rong, Xiaochun},
   title={A connectedness principle in the geometry of positive curvature},
   journal={Comm. Anal. Geom.},
   volume={13},
   date={2005},
   number={4},
   pages={671--695},
   %issn={1019-8385},
   %review={\MR{2191903 (2007h:53049)}},
}

\bib{fary}{article}{
   author={F{\'a}ry, Istv{\'a}n},
   title={Sur certaines in\'egalites g\'eom\'etriques},
   %language={French},
   journal={Acta Sci. Math. Szeged},
   volume={12},
   date={1950},
   number={Leopoldo Fejer et Frederico Riesz LXX annos natis dedicatus, Pars
   A},
   pages={117--124},
   %issn={0001-6969},
   %review={\MR{0038090 (12,353b)}},
}

\bib{ferry-okun}{article}{
   author={Ferry, Steven C.},
   author={Okun, Boris L.},
   title={Approximating topological metrics by Riemannian metrics},
   journal={Proc. Amer. Math. Soc.},
   volume={123},
   date={1995},
   number={6},
   pages={1865--1872},
   %issn={0002-9939},
   %review={\MR{1246524 (95g:53050)}},
   %doi={10.2307/2161004},
}

\bib{foertsch-schroeder}{article}{
   author={Foertsch, Thomas},
   author={Schroeder, Viktor},
   title={Minkowski versus Euclidean rank for products of metric spaces},
   journal={Adv. Geom.},
   volume={2},
   date={2002},
   number={2},
   pages={123--131},
   %issn={1615-715X},
   %review={\MR{1895343 (2003c:53052)}},
   %doi={10.1515/advg.2002.002},
}

\bib{frankel-katz}{article}{
   author={Frankel, S.},
   author={Katz, M.},
   title={The Morse landscape of a Riemannian disk},
   %language={English, with English and French summaries},
   journal={Ann. Inst. Fourier (Grenoble)},
   volume={43},
   date={1993},
   number={2},
   pages={503--507},
   %issn={0373-0956},
   %review={\MR{1220281 (94c:53057)}},
}

\bib{frankel}{article}{
   author={Frankel, T.},
   title={On the fundamental group of a compact minimal submanifold},
   journal={Ann. of Math. (2)},
   volume={83},
   date={1966},
   pages={68--73},
   %issn={0003-486X},
   %review={\MR{0187183 (32 \#4637)}},
}

\bib{frechet}{article}{
Author = {M. Fr\'echet},
Title = {Les ensembles abstraits et le calcul fonctionnel.},
Journal = {Rendiconti del Circolo Matematico di Palermo},
   % Journal = {{Rend. Circ. Mat. Palermo}},
    %ISSN = {0009-725X; 1973-4409/e},
    Volume = {30},
    Pages = {1--26},
    Year = {1910},
    Publisher = {Circolo Matematico, Palermo},
    %Language = {French},
    %DOI = {10.1007/BF03014860},
    %Zbl = {41.0103.01}
}

\bib{galperin}{article}{
   author={Galperin, G.},
   title={Convex polyhedra without simple closed geodesics},
   journal={Regul. Chaotic Dyn.},
   volume={8},
   date={2003},
   number={1},
   pages={45--58},
   %issn={1560-3547},
   %review={\MR{1963967 (2004c:37085)}},
   %doi={10.1070/RD2003v008n01ABEH000231},
}

\bib{GKZ}{book}{
   author={Gelfand, I. M.},
   author={Kapranov, M. M.},
   author={Zelevinsky, A. V.},
   title={Discriminants, resultants and multidimensional determinants},
   series={Modern Birkh\"auser Classics},
   %note={Reprint of the 1994 edition},
   %publisher={Birkh\"auser Boston, Inc., Boston, MA},
   date={2008},
   %pages={x+523},
   %isbn={978-0-8176-4770-4},
   %review={\MR{2394437 (2009a:14065)}},
}

\bib{ginzburg}{article}{
   author={Ginzburg, Viktor L.},
   title={On the existence and non-existence of closed trajectories for some
   Hamiltonian flows},
   journal={Math. Z.},
   volume={223},
   date={1996},
   number={3},
   pages={397--409},
   %issn={0025-5874},
   %review={\MR{1417851 (97i:58144)}},
   %doi={10.1007/PL00004565},
}

\bib{greene-wu}{article}{
   author={Greene, R. E.},
   author={Wu, H.},
   title={On the subharmonicity and plurisubharmonicity of geodesically
   convex functions},
   journal={Indiana Univ. Math. J.},
   volume={22},
   date={1972/73},
   pages={641--653},
   %issn={0022-2518},
   %review={\MR{0422686 (54 \#10672)}},
}

\bib{GKM}{book}{
   author={Gromoll, D.},
   author={Klingenberg, W.},
   author={Meyer, W.},
   title={Riemannsche Geometrie im Grossen},
   %language={German},
   series={Lecture Notes in Mathematics, No. 55},
   publisher={Springer-Verlag, Berlin-New York},
   date={1968},
   pages={vi+287},
   %review={\MR{0229177 (37 \#4751)}},
}

\bib{gromoll-meyer}{article}{
   author={Gromoll, Detlef},
   author={Meyer, Wolfgang},
   title={An exotic sphere with nonnegative sectional curvature},
   journal={Ann. of Math. (2)},
   volume={100},
   date={1974},
   pages={401--406},
   %issn={0003-486X},
   %review={\MR{0375151 (51 \#11347)}},
}

\bib{gromov-almost-flat}{article}{
   author={Gromov, Mikhael},
   title={Almost flat manifolds},
   journal={J. Differential Geom.},
   volume={13},
   date={1978},
   number={2},
   pages={231--241},
   %issn={0022-040X},
   %review={\MR{540942 (80h:53041)}},
}

\bib{gromov-hyperbolic}{article}{
   author={Gromov, Mikhael},
   title={Hyperbolic manifolds, groups and actions},
   conference={
      title={Riemann surfaces and related topics: Proceedings of the 1978
      Stony Brook Conference},
      address={State Univ. New York, Stony Brook, N.Y.},
      date={1978},
   },
   book={
      series={Ann. of Math. Stud.},
      volume={97},
      publisher={Princeton Univ. Press, Princeton, N.J.},
   },
   date={1981},
   pages={183--213},
  % review={\MR{624814 (82m:53035)}},
}

\bib{gromov-filling}{article}{
   author={Gromov, Mikhael},
   title={Filling Riemannian manifolds},
   journal={J. Differential Geom.},
   volume={18},
   date={1983},
   number={1},
   pages={1--147},
   %issn={0022-040X},
   %review={\MR{697984 (85h:53029)}},
}

\bib{gromov-lawson}{article}{
   author={Gromov, Mikhael},
   author={Lawson, H. Blaine, Jr.},
   title={Positive scalar curvature and the Dirac operator on complete
   Riemannian manifolds},
   journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
   number={58},
   date={1983},
   pages={83--196 (1984)},
   %issn={0073-8301},
   %review={\MR{720933 (85g:58082)}},
}

\bib{gromov-pseudoholomorphic}{article}{
   author={Gromov, Mikhael},
   title={Pseudoholomorphic curves in symplectic manifolds},
   journal={Invent. Math.},
   volume={82},
   date={1985},
   number={2},
   pages={307--347},
   %issn={0020-9910},
   %review={\MR{809718 (87j:53053)}},
   %doi={10.1007/BF01388806},
}

\bib{gromov-PDR}{book}{
   author={Gromov, Mikhael},
   title={Partial differential relations},
   series={Ergebnisse der Mathematik und ihrer Grenzgebiete (3) [Results in
   Mathematics and Related Areas (3)]},
   volume={9},
   %publisher={Springer-Verlag, Berlin},
   date={1986},
   pages={x+363},
   %isbn={3-540-12177-3},
   %review={\MR{864505 (90a:58201)}},
   %doi={10.1007/978-3-662-02267-2},
}

\bib{gromov-SGMC}{article}{
   author={Gromov, Mikhael},
   title={Sign and geometric meaning of curvature},
   %language={English, with English and Italian summaries},
   journal={Rend. Sem. Mat. Fis. Milano},
   volume={61},
   date={1991},
   pages={9--123},
   %issn={0370-7377},
   %review={\MR{1297501 (95j:53055)}},
   %doi={10.1007/BF02925201},
}

\bib{gromov-MetStr}{book}{
   author={Gromov, Mikhael},
   title={Metric structures for Riemannian and non-Riemannian spaces},
   series={Modern Birkh\"auser Classics},
   %edition={Reprint of the 2001 English edition},
   %note={Based on the 1981 French original; With appendices by M. Katz, P. Pansu and S. Semmes; Translated from the French by Sean Michael Bates},
   %publisher={Birkh\"auser Boston, Inc., Boston, MA},
   date={2007},
   %pages={xx+585},
   %isbn={978-0-8176-4582-3},
   %isbn={0-8176-4582-9},
   %review={\MR{2307192 (2007k:53049)}},
}

\bib{grove}{article}{
   author={Grove, Karsten},
   title={Geometry of, and via, symmetries},
   conference={
      title={Conformal, Riemannian and Lagrangian geometry (Knoxville, TN,
      2000)},
   },
   book={
      series={Univ. Lecture Ser.},
      volume={27},
      %publisher={Amer. Math. Soc., Providence, RI},
   },
   date={2002},
   pages={31--53},
   %review={\MR{1922721 (2003g:53046)}},
}

\bib{grove-wilking}{article}{
   author={Grove, Karsten},
   author={Wilking, Burkhard},
   title={A knot characterization and 1--connected nonnegatively curved
   4--manifolds with circle symmetry},
   journal={Geom. Topol.},
   volume={18},
   date={2014},
   number={5},
   pages={3091--3110},
   %issn={1465-3060},
   %review={\MR{3285230}},
   %doi={10.2140/gt.2014.18.3091},
}

\bib{guth-symplectic}{article}{
   author={Guth, Larry},
   title={Symplectic embeddings of polydisks},
   journal={Invent. Math.},
   volume={172},
   date={2008},
   number={3},
   pages={477--489},
   %issn={0020-9910},
   %review={\MR{2393077 (2008k:53195)}},
   %doi={10.1007/s00222-007-0103-9},
}

\bib{guzhvina}{article}{
   author={G.~Guzhvina},
   title={Gromov's pinching constant},
   journal={\tt arXiv:0804.0201 [math.DG]},
}

\bib{hang-wang}{article}{
   author={Hang, Fengbo},
   author={Wang, Xiaodong},
   title={Rigidity theorems for compact manifolds with boundary and positive
   Ricci curvature},
   journal={J. Geom. Anal.},
   volume={19},
   date={2009},
   number={3},
   pages={628--642},
   %issn={1050-6926},
   %review={\MR{2496569 (2010k:53065)}},
   %doi={10.1007/s12220-009-9074-y},
}

\bib{halberg-levin-straus}{article}{
   author={Halberg, Charles J. A., Jr.},
   author={Levin, Eugene},
   author={Straus, E. G.},
   title={On contiguous congruent sets in Euclidean space},
   journal={Proc. Amer. Math. Soc.},
   volume={10},
   date={1959},
   pages={335--344},
   %issn={0002-9939},
   %review={\MR{0106438 (21 \#5170)}},
}

\bib{hamkins}{misc}{    
    title={Is the sphere the only surface all of whose projections are circles? Or: Can we deduce a spherical Earth by observing that its shadows on the Moon are always circular?},    
    author={Joel David Hamkins},    
    note={Question 39127},    
    eprint={http://mathoverflow.net/q/39127},    
    organization={MathOverflow}  
}

\bib{harnack}{article}{
   author={Harnack, Axel},
   title={Ueber die Vieltheiligkeit der ebenen algebraischen Curven},
   language={German},
   journal={Math. Ann.},
   volume={10},
   date={1876},
   number={2},
   pages={189--198},
   %issn={0025-5831},
   %review={\MR{1509883}},
   %doi={10.1007/BF01442458},
}

\bib{hilbert}{article}{
   author={Hilbert, David},
   title={Ueber die gerade Linie als k\"urzeste Verbindung zweier Punkte},
   %language={German},
   journal={Math. Ann.},
   volume={46},
   date={1895},
   number={1},
   pages={91--96},
   %issn={1432-1807},
   %doi={10.1007/BF02096204},
}

\bib{hilbert-problems}{article}{
   author={Hilbert, David},
   title={Mathematical problems},
   journal={Bull. Amer. Math. Soc.},
   volume={8},
   date={1902},
   number={10},
   pages={437--479},
   %issn={0002-9904},
   %review={\MR{1557926}},
   %doi={10.1090/S0002-9904-1902-00923-3},
}

\bib{hitzelberger-lytchak}{article}{
   author={Hitzelberger, Petra},
   author={Lytchak, Alexander},
   title={Spaces with many affine functions},
   journal={Proc. Amer. Math. Soc.},
   volume={135},
   date={2007},
   number={7},
   pages={2263--2271},
   %issn={0002-9939},
   %review={\MR{2299504 (2008g:53045)}},
   %doi={10.1090/S0002-9939-07-08728-X},
}

\bib{honda}{article}{
   author={Honda, Ko},
   title={Transversality theorems for harmonic forms},
   journal={Rocky Mountain J. Math.},
   volume={34},
   date={2004},
   number={2},
   pages={629--664},
   %issn={0035-7596},
   %review={\MR{2072799 (2005f:58052)}},
   %doi={10.1216/rmjm/1181069872},
}

\bib{hsiang-kleiner}{article}{
   author={Hsiang, Wu-Yi},
   author={Kleiner, Bruce},
   title={On the topology of positively curved $4$-manifolds with symmetry},
   journal={J. Differential Geom.},
   volume={29},
   date={1989},
   number={3},
   pages={615--621},
   %issn={0022-040X},
   %review={\MR{992332 (90e:53053)}},
}

\bib{imre-kuiperberg-zamfirescu}{article}{
   author={B{\'a}r{\'a}ny, Imre},
   author={Kuperberg, Krystyna},
   author={Zamfirescu, Tudor},
   title={Total curvature and spiralling shortest paths},
   %note={U.S.-Hungarian Workshops on Discrete Geometry and Convexity
   %(Budapest, 1999/Auburn, AL, 2000)},
   journal={Discrete Comput. Geom.},
   volume={30},
   date={2003},
   number={2},
   pages={167--176},
   %issn={0179-5376},
   %review={\MR{2007957 (2004h:52009)}},
   %doi={10.1007/s00454-003-0001-z},
}

\bib{izmestiev-rote-springborn-kusner}{article}{
   author={Izmestiev, Ivan},
   author={Kusner, Robert B.},
   author={Rote, G{\"u}nter},
   author={Springborn, Boris},
   author={Sullivan, John M.},
   title={There is no triangulation of the torus with vertex degrees
   $5,6,\dots,6,7$ and related results: geometric proofs for combinatorial
   theorems},
   journal={Geom. Dedicata},
   volume={166},
   date={2013},
   pages={15--29},
   %issn={0046-5755},
   %review={\MR{3101158}},
   %doi={10.1007/s10711-012-9782-5},
}

\bib{jendrol-jucovich}{article}{
   author={Jendrol{\soft{l}}, S.},
   author={Jucovi{\v{c}}, E.},
   title={On the toroidal analogue of Eberhard's theorem},
   journal={Proc. London Math. Soc. (3)},
   volume={25},
   date={1972},
   pages={385--398},
   %issn={0024-6115},
   %review={\MR{0307968 (46 \#7083)}},
}

\bib{kirby}{article}{
   author={Kirby, Robion C.},
   title={Stable homeomorphisms and the annulus conjecture},
   journal={Ann. of Math. (2)},
   volume={89},
   date={1969},
   pages={575--582},
   %issn={0003-486X},
   %review={\MR{0242165 (39 \#3499)}},
}

\bib{kirszbraun}{article}{
    author = {M. D. Kirszbraun},
    title = {\"Uber die zusammenziehenden und Lipschitzschen Transformationen.},
    journal = {Fundam. Math.},
    %ISSN = {0016-2736; 1730-6329/e},
    volume = {22},
    pages = {77--108},
    date = {1934},
    publisher = {Polish Academy of Sciences (Polska Akademia Nauk - PAN), Institute of Mathematics (Instytut Matematyczny), Warsaw},
    %language = {German},
    %Zbl = {0009.03904}
}

\bib{klee}{article}{
   author={Klee, V. L., Jr.},
   title={Some topological properties of convex sets},
   journal={Trans. Amer. Math. Soc.},
   volume={78},
   date={1955},
   pages={30--45},
   %issn={0002-9947},
   %review={\MR{0069388 (16,1030c)}},
}

\bib{knaster}{article}{
author = {B. Knaster},
title = {Un continu dont tout sous-continu est ind\'ecomposable.},
journal = {Fundamenta Mathematicae},
volume = {3},
pages = {247--286},
year = {1922},
publisher = {Polish Academy of Sciences (Polska Akademia Nauk - PAN), Institute of Mathematics (Instytut Matematyczny), Warsaw}
    %Zbl = {48.0212.01}
}

\bib{knaster}{article}{
Author = {Knaster, B.},
Title = {Un continu dont tout sous-continu est ind\'ecomposable.},
Journal = {{Fundamenta Mathematicae}},
%Journal = {{Fundam. Math.}},
%ISSN = {0016-2736; 1730-6329/e},
    Volume = {3},
    Pages = {247--286},
    Year = {1922}
%Publisher = {Polish Academy of Sciences (Polska Akademia Nauk - PAN), Institute of Mathematics (Instytut Matematyczny), Warsaw},
%Language = {French},
%Zbl = {48.0212.01}
}

\bib{kneser}{article}{
   author={Kneser, A.},
   title={Bemerkungen \"uber die Anzahl der Extreme der Kr\"ummung
auf geschlossenen Kurven und \"uber vertwandte Fragen in einer nichteuklidischen
Geometrie},
   journal={Festschrift H. Weber},
   date={1912},
   pages={170--180},
}

\bib{krat}{thesis}
{author={S.~Krat},
title={Approximation Problems in Length Geometry},
address={Pennsylvania State University},
date={2005},
type={Ph.D. thesis},
}

\bib{kuiper}{article}{
   author={Kuiper, Nicolaas H.},
   title={On $C^1$-isometric imbeddings. I, II},
   journal={Nederl. Akad. Wetensch. Proc. Ser. A. {\bf 58} = Indag. Math.},
   volume={17},
   date={1955},
   pages={545--556, 683--689},
   %review={\MR{0075640 (17,782c)}},
}

\bib{kuratowski}{article}{
    Author = {Kuratowski, Casimir},
    Title = {Quelques probl\`emes concernant les espaces m\'etriques nonseparables.},
    Journal = {Fundamenta Mathematicae},
    %Journal = {{Fundam. Math.}},
    %ISSN = {0016-2736; 1730-6329/e},
    Volume = {25},
    Pages = {534--545},
    Year = {1935},
    Publisher = {Polish Academy of Sciences (Polska Akademia Nauk - PAN), Institute of Mathematics (Instytut Matematyczny), Warsaw}
    %Language = {French},
   % Zbl = {0012.32103}
}

\bib{kwun}{article}{
   author={Kwun, Kyung Whan},
   title={Uniqueness of the open cone neighborhood},
   journal={Proc. Amer. Math. Soc.},
   volume={15},
   date={1964},
   pages={476--479},
   %issn={0002-9939},
   %review={\MR{0161319 (28 \#4527)}},
}

\bib{mccord}{article}{
   author={McCord, Michael C.},
   title={Singular homology groups and homotopy groups of finite topological
   spaces},
   journal={Duke Math. J.},
   volume={33},
   date={1966},
   pages={465--474},
   %issn={0012-7094},
   %review={\MR{0196744 (33 \#4930)}},
}

\bib{milnor}{article}{
   author={Milnor, J. W.},
   title={On the total curvature of knots},
   journal={Ann. of Math. (2)},
   volume={52},
   date={1950},
   pages={248--257},
   issn={0003-486X},
   review={\MR{0037509 (12,273c)}},
}

\bib{montgomery}{article}{
   author={Montgomery, Deane},
   title={Pointwise Periodic Homeomorphisms},
   journal={Amer. J. Math.},
   volume={59},
   date={1937},
   number={1},
   pages={118--120},
   %issn={0002-9327},
   %review={\MR{1507223}},
   %doi={10.2307/2371565},
}

\bib{nabutovsky-NovThm}{article}{
   author={Nabutovsky, A.},
   title={Einstein structures: existence versus uniqueness},
   journal={Geom. Funct. Anal.},
   volume={5},
   date={1995},
   number={1},
   pages={76--91},
   %issn={1016-443X},
   %review={\MR{1312020 (96e:53061)}},
   %doi={10.1007/BF01928216},
}

\bib{nabutovsky-Disconnectedness}{article}{
   author={Nabutovsky, A.},
   title={Disconnectedness of sublevel sets of some Riemannian functionals},
   journal={Geom. Funct. Anal.},
   volume={6},
   date={1996},
   number={4},
   pages={703--725},
   %issn={1016-443X},
   %review={\MR{1406670 (97i:58018)}},
   %doi={10.1007/BF02247118},
}


\bib{newman}{article}{
author = {M. H. A. Newman},
title = {A theorem on periodic transformations of spaces.},
journal = {The Quarterly Journal of Mathematics. Oxford Series},
 %   Journal = {{Q. J. Math., Oxf. Ser.}},
    %ISSN = {0033-5606},
    Volume = {2},
    Pages = {1--8},
    Year = {1931},
    Publisher = {Oxford University Press, Oxford}
    %Language = {English},
    %Zbl = {57.0496.02}
}

\bib{lagarias-richardson}{article}{
   author={Lagarias, Jeffrey C.},
   author={Richardson, Thomas J.},
   title={Convexity and the average curvature of plane curves},
   journal={Geom. Dedicata},
   volume={67},
   date={1997},
   number={1},
   pages={1--30},
   %issn={0046-5755},
   %review={\MR{1468858 (98f:52007)}},
   %doi={10.1023/A:1004912521664},
}

\bib{lange}{article}{
author={Lange, Christian},
title={When is the underlying space of an orbifold a topological manifold},
journal={\tt arXiv:1307.4875 [math.GN]},
}

\bib{lebedeva-petrunin}{article}
{author={Lebedeva, N.},
author={Petrunin, A.},
title={Local characterization of polyhedral spaces},
journal={Geometriae Dedicata (to appear) \tt arXiv:1402.6670 [math.DG]}
} 

\bib{le-donne}{article}{
   author={Le Donne, Enrico},
   title={Lipschitz and path isometric embeddings of metric spaces},
   journal={Geom. Dedicata},
   volume={166},
   date={2013},
   pages={47--66},
   %issn={0046-5755},
   %review={\MR{3101160}},
   %doi={10.1007/s10711-012-9785-2},
}


\bib{liberman}{article}{
   author={Liberman, J.},
   title={Geodesic lines on convex surfaces},
   journal={C. R. (Doklady) Acad. Sci. URSS (N.S.)},
   volume={32},
   date={1941},
   pages={310--313},
   %review={\MR{0010994 (6,100g)}},
}

\bib{lobachevsky}{book}{
author={Lobachevsky, N. I.}, 
title={Geometrische Untersuchungen zur Theorie der Parallellinien},
publisher={Berlin: F. Fincke},
date={1840}
}

\bib{matveyev}{article}
{author={Rostislav Matveev},
title={Surfaces with polyhedral metrics},
conference={
      title={International Mathematical Summer School for Students 2011},
      address={Jacobs University, Bremen},
   },
}

\bib{micallef-moore}{article}{
   author={Micallef, Mario J.},
   author={Moore, John Douglas},
   title={Minimal two-spheres and the topology of manifolds with positive
   curvature on totally isotropic two-planes},
   journal={Ann. of Math. (2)},
   volume={127},
   date={1988},
   number={1},
   pages={199--227},
   %issn={0003-486X},
   %review={\MR{924677 (89e:53088)}},
   %doi={10.2307/1971420},
}

\bib{mikhailova}{article}{
   author={Mikha{\u\i}lova, M. A.},
   title={A factor space with respect to the action of a finite group
   generated by pseudoreflections},
   %language={Russian},
   journal={Izv. Akad. Nauk SSSR Ser. Mat.},
   volume={48},
   date={1984},
   number={1},
   pages={104--126},
   %issn={0373-2436},
   %review={\MR{733360 (85k:20127)}},
}

\bib{milka-poly}{article}{
   author={Milka, A. D.},
   title={Multidimensional spaces with polyhedral metric of nonnegative
   curvature. I},
   %language={Russian},
   journal={Ukrain. Geometr. Sb. Vyp.},
   volume={5--6},
   date={1968},
   pages={103--114},
   %review={\MR{0286057 (44 \#3273)}},
}

\bib{milka-geod}{article}{
   author={Milka, A. D.},
   title={Shortest lines on convex surfaces},
   %language={Russian},
   journal={Dokl. Akad. Nauk SSSR},
   volume={248},
   date={1979},
   number={1},
   pages={34--36},
   %issn={0002-3264},
   %review={\MR{549365 (81c:53056)}},
}

\bib{gromov-apendix}{book}{
   author={Milman, Vitali D.},
   author={Schechtman, Gideon},
   title={Asymptotic theory of finite-dimensional normed spaces},
   series={Lecture Notes in Mathematics},
   volume={1200},
   note={With an appendix by M. Gromov},
   publisher={Springer-Verlag, Berlin},
   date={1986},
   pages={viii+156},
   %isbn={3-540-16769-2},
   %review={\MR{856576 (87m:46038)}},
}

\bib{hall}{article}{
   author={Hall, Marshall, Jr.},
   title={Subgroups of finite index in free groups},
   journal={Canadian J. Math.},
   volume={1},
   date={1949},
   pages={187--190},
   %issn={0008-414X},
   %review={\MR{0028836 (10,506a)}},
}

\bib{wayne}{article}{
   author={Lewis, Wayne},
   title={The pseudo-arc},
   journal={Bol. Soc. Mat. Mexicana (3)},
   volume={5},
   date={1999},
   number={1},
   pages={25--77},
   %issn={1405-213X},
   %review={\MR{1692467 (2000f:54029)}},
}

\bib{lohkamp}{article}{
   author={Lohkamp, Joachim},
   title={Metrics of negative Ricci curvature},
   journal={Ann. of Math. (2)},
   volume={140},
   date={1994},
   number={3},
   pages={655--683},
   %issn={0003-486X},
   %review={\MR{1307899 (95i:53042)}},
   %doi={10.2307/2118620},
}

\bib{mazur-ulam}{article}{
   author={Mazur, S.},
   author={Ulam, S.},
   title={Sur les transformations isom\'etriques d'espaces vectoriels norm\'es},
   %language={French},
   journal={C. R. Acad. Sci., Paris},
   volume={194},
   date={1932},
   number={1},
   pages={946--948},
   %issn={0026-9255},
   %review={\MR{1550413}},
   %doi={10.1007/BF01733278},
}

\bib{monsky}{article}{
   author={Monsky, Paul},
   title={On dividing a square into triangles},
   journal={Amer. Math. Monthly},
   volume={77},
   date={1970},
   pages={161--164},
   %issn={0002-9890},
   %review={\MR{0252233 (40 \#5454)}},
}

\bib{nabutovsky-rotman}{article}{
   author={Nabutovsky, Alexander},
   author={Rotman, Regina},
   title={Length of geodesics and quantitative Morse theory on loop spaces},
   journal={Geom. Funct. Anal.},
   volume={23},
   date={2013},
   number={1},
   pages={367--414},
   %issn={1016-443X},
   %review={\MR{3037903}},
   %doi={10.1007/s00039-012-0207-2},
}

\bib{nash}{article}{
   author={Nash, John},
   title={$C^1$ isometric imbeddings},
   journal={Ann. of Math. (2)},
   volume={60},
   date={1954},
   pages={383--396},
   %issn={0003-486X},
   %review={\MR{0065993 (16,515e)}},
}

\bib{osgood}{article}{
   author={Osgood, William F.},
   title={A Jordan curve of positive area},
   journal={Trans. Amer. Math. Soc.},
   volume={4},
   date={1903},
   number={1},
   pages={107--112},
   %issn={0002-9947},
   %review={\MR{1500628}},
   %doi={10.2307/1986455},
}

\bib{ovsienko-tabachnikov}{book}{
   author={Ovsienko, V.},
   author={Tabachnikov, S.},
   title={Projective differential geometry old and new},
   series={Cambridge Tracts in Mathematics},
   volume={165},
   %note={From the Schwarzian derivative to the cohomology of diffeomorphism groups},
   publisher={Cambridge University Press, Cambridge},
   date={2005},
   %pages={xii+249},
   %isbn={0-521-83186-5},
   %review={\MR{2177471 (2007b:53017)}},
}

\bib{rourke}{misc}{    
    title={Why is the half-torus rigid?},    
    author={Joseph O'Rourke},    
    note={Question 77760},    
    eprint={http://mathoverflow.net/q/77760},    
    organization={MathOverflow}  
}

\bib{panov-Kaeler}{article}{
   author={Panov, Dmitri},
   title={Polyhedral K\"ahler manifolds},
   journal={Geom. Topol.},
   volume={13},
   date={2009},
   number={4},
   pages={2205--2252},
   %issn={1465-3060},
   %review={\MR{2507118 (2010f:53129)}},
   %doi={10.2140/gt.2009.13.2205},
}

\bib{panov-torus}{article}{
   author={Panov, Dmitri},
   title={Foliations with unbounded deviation on $\mathbb{T}^2$},
   journal={J. Mod. Dyn.},
   volume={3},
   date={2009},
   number={4},
   pages={589--594},
   %issn={1930-5311},
   %review={\MR{2587087 (2011d:37046)}},
   %doi={10.3934/jmd.2009.3.589},
}

\bib{panov-curves}{article}{
   author={Panov, Dmitri},
   title={Parabolic curves and gradient mappings},
      journal={Proc. Steklov Inst. Math.},
      date={1998},
      number={2 (221)},
      pages={261--278},
      issn={0081-5438},
   %review={\MR{1683700 (2000c:53085)}},
}

\bib{panov-petrunin-telescopic}{article}{
   author={Panov, Dmitri},
   author={Petrunin, Anton},
   title={Telescopic actions},
   journal={Geom. Funct. Anal.},
   volume={22},
   date={2012},
   number={6},
   pages={1814--1831},
   %issn={1016-443X},
   %review={\MR{3000502}},
   %doi={10.1007/s00039-012-0194-3},
}


\bib{panov-petrunin}{article}{
   author={Panov, Dmitri},
   author={Petrunin, Anton},
   title={Sweeping out sectional curvature},
   journal={Geom. Topol.},
   volume={18},
   date={2014},
   number={2},
   pages={617--631},
   %issn={1465-3060},
   %review={\MR{3159972}},
   %doi={10.2140/gt.2014.18.617},
}

\bib{panov-petrunin-ramification}{article}{
   author={Panov, Dmitri},
   author={Petrunin, Anton},
   title={Ramification conjecture and Hirzebruch's property of line arrangements},
   journal={{\tt arXiv:1312.6856 [math.GT]}},
}

\bib{perelman}{article}{
   author={Perelman, G.},
   title={Proof of the soul conjecture of Cheeger and Gromoll},
   journal={J. Differential Geom.},
   volume={40},
   date={1994},
   number={1},
   pages={209--212},
   %issn={0022-040X},
   %review={\MR{1285534 (95d:53037)}},
}

\bib{two-discs}{misc}{    
title={Two discs with no parallel tangent planes},    
author={Petrunin, Anton},    
note={Question 17486}, 
eprint={http://mathoverflow.net/q/17486},    
organization={MathOverflow}
}

\bib{One-step problems in geometry}{misc}{    
    title={One-step problems in geometry},    
    author={Petrunin, Anton},    
    note={Question 8247},    
    eprint={http://mathoverflow.net/q/8247},    
    organization={MathOverflow}  
}

\bib{ivanov}{misc}{    
    title={Diameter of m-fold cover},    
    author={Petrunin, Anton},    
    note={Question 7732},    
    eprint={http://mathoverflow.net/q/7732},    
    organization={MathOverflow}  
}

\bib{petrunin-paths}{article}{
   author={Petrunin, Anton},
   title={Intrinsic isometries in Euclidean space},
      journal={St. Petersburg Math. J.},
      volume={22},
      date={2011},
      number={5},
      pages={803--812},
      %issn={1061-0022},
   %review={\MR{2828830 (2012e:54037)}},
   %doi={10.1090/S1061-0022-2011-01169-0},
}

\bib{petrunin-monthly}{article}{
   author={Petrunin, Anton},
   title={Area Minimizing Polyhedral Surfaces are Saddle},
   journal={Amer. Math. Monthly},
   volume={122},
   date={2015},
   number={3},
   pages={264--267},
   %issn={0002-9890},
   %review={\MR{3327716}},
   %doi={10.4169/amer.math.monthly.122.03.264},
}

\bib{petrunin-yashinsky}{article}{
   author={Petrunin, Anton},
   author={Yashinski, Allan},
   title={Piecewise distance preserving maps},
   journal={to appear in St. Petersburg Mathematical Journal.},
}

\bib{pogorelov}{book}{
   author={Pogorelov, Aleksei},
   title={Hilbert's fourth problem},
   %note={Translated by Richard A. Silverman;
   %Scripta Series in Mathematics},
   publisher={V. H. Winston \& Sons, Washington, D.C.; A Halsted Press Book,
   John Wiley \& Sons, New York-Toronto, Ont.-London},
   date={1979},
   pages={vi+97},
   %isbn={0-470-26735-6},
   %review={\MR{550440 (80j:53066)}},
}

\bib{poincare}{article}{
author={H. Poincar\'e},
title={Sur un th\'{e}or\`{e}me de g\'{e}ometrie}, 
journal={Rend. Circ. Mat. Palermo}, 
volume={33},
date={1912},
pages={75--407}
}

\bib{three-discs}{misc}{    
    title={A generalization of Cauchy's mean value theorem},    
    author={Petya Pushkar},    
    note={Question 16335},    
    eprint={http://mathoverflow.net/q/16335},    
    organization={MathOverflow}  
}

\bib{rademacher}{article}{
   author={Rademacher, Hans},
   title={\"Uber partielle und totale differenzierbarkeit von Funktionen
   mehrerer Variabeln und \"uber die Transformation der Doppelintegrale},
   %language={German},
   journal={Math. Ann.},
   volume={79},
   date={1919},
   number={4},
   pages={340--359},
   %issn={0025-5831},
   %review={\MR{1511935}},
   %doi={10.1007/BF01498415},
}

\bib{rembs}{article}{
    author = {Eduard Rembs},
    title = {Verbiegungen h\"oherer Ordnung und ebene Fl\"achenrinnen.},
    %FJournal = {Mathematische Zeitschrift},
    journal = {Math. Z.},
    %ISSN = {0025-5874; 1432-1823/e},
    volume = {36},
    pages = {110--121},
    date = {1932},
    publisher = {Springer, Berlin/Heidelberg},
    %Language = {German},
    %DOI = {10.1007/BF01188611},
    %Zbl = {0005.02401}
}

\bib{ruh}{article}{
   author={Ruh, Ernst A.},
   title={Almost flat manifolds},
   journal={J. Differential Geom.},
   volume={17},
   date={1982},
   number={1},
   pages={1--14},
   %issn={0022-040X},
   %review={\MR{658470 (84a:53047)}},
}

\bib{sabitov}{article}{
   author={Sabitov, I. H.},
   title={Infinitesimal bendings of troughs of revolution. I},
   %language={Russian},
   journal={Mat. Sb. (N.S.)},
   volume={98(140)},
   date={1975},
   number={1 (9)},
   pages={113--129, 159},
   %review={\MR{0405299 (53 \#9093)}},
}

\bib{sahovic}{thesis}
{author={V.~Sahovic},
title={Approximations of Riemannian Manifolds with Linear Curvature Constraints},
address={Westf\"alische Wilhelms-Universit\"at M\"unster},
date={2009},
type={Dissertation},
}

\bib{schoen-yau}{article}{
   author={Schoen, R.},
   author={Yau, Shing Tung},
   title={Existence of incompressible minimal surfaces and the topology of
   three-dimensional manifolds with nonnegative scalar curvature},
   journal={Ann. of Math. (2)},
   volume={110},
   date={1979},
   number={1},
   pages={127--142},
   %issn={0003-486X},
   %review={\MR{541332 (81k:58029)}},
   %doi={10.2307/1971247},
}

\bib{siebenmann}{article}{
   author={Siebenmann, L. C.},
   title={Deformation of homeomorphisms on stratified sets. I, II},
   journal={Comment. Math. Helv.},
   volume={47},
   date={1972},
   pages={123--136; 137--163},
   %issn={0010-2571},
   %review={\MR{0319207 (47 \#7752)}},
}

\bib{shen}{article}{
author={Shen, A.},
title={Unexpected proofs},
subtitle={Boxes in a Train},
pages={48--50},
journal={Math. Intelligencer},
volume={21},
date={1999},
number={3}
}

%\bib{shor-van wyk}{article}{
%   author={Shor, Peter W.},
%   author={Van Wyk, Christopher J.},
%   title={Detecting and decomposing self-overlapping curves},
%   journal={Comput. Geom.},
%   volume={2},
%   date={1992},
%   number={1},
%   pages={31--50},
   %issn={0925-7721},
   %review={\MR{1186078 (93i:68183)}},
   %doi={10.1016/0925-7721(92)90019-O},
%}

\bib{stallings}{article}{
   author={Stallings, John R.},
   title={Topology of finite graphs},
   journal={Invent. Math.},
   volume={71},
   date={1983},
   number={3},
   pages={551--565},
   %issn={0020-9910},
   %review={\MR{695906 (85m:05037a)}},
   %doi={10.1007/BF02095993},
}

\bib{sullivan}{article}{
   author={Sullivan, Dennis},
   title={Hyperbolic geometry and homeomorphisms},
   conference={
      title={Geometric topology (Proc. Georgia Topology Conf., Athens, Ga.,
      1977)},
   },
   book={
      %publisher={Academic Press, New York-London},
   },
   date={1979},
   pages={543--555},
   %review={\MR{537749 (81m:57012)}},
}

\bib{synge}{article}{
Author = {J. L. Synge},
Title = {On the connectivity of spaces of positive curvature},
Year = {1937},
%Language = {English},
journal = {C. R. Congr. internat. Math., Oslo 1936,},
volume={2},
date={1937},
pages={138--139}
    %Zbl = {63.0710.05}
}

\bib{tabachnikov}{article}{
   author={Tabachnikov, Serge},
   title={The tale of a geometric inequality},
   conference={
      title={MASS selecta},
   },
   book={
      publisher={Amer. Math. Soc., Providence, RI},
   },
   date={2003},
   pages={257--262},
   %review={\MR{2027183}},
}

\bib{tabachnikob-mi}{article}
{author={Tabachnikov, Serge},
title={Supporting cords of convex sets},
subtitle={Problem 91-2 in Mathematical Entertainments},
journal={Mathematical Intelligencer},
volume={13},
number={1},
pages={33},
date={Winter 1991}
}


\bib{tabacnikov=tan}{article}{
   author={Tabachnikov, Serge},
   journal={The American Mathematical Monthly},
   title={The (Un)equal Tangents Problem},
   volume={119},
   number={5},
   date={May 2012},
   pages={398--405},
   %review={\MR{2027183}},
}

\bib{tait}{article}{
   author={Tait, P.},%Peter Guthrie Tait
   title={Note on the circles of curvature of a plane curve},
   journal={Proc. Edinburgh Math. Soc.},
   volume={14},
   date={February 1895},
   pages={26},
}

\bib{toponogov}{article}{
   author={Toponogov, V. A.},
   title={Evaluation of the length of a closed geodesic on a convex surface},
   %language={Russian},
   journal={Dokl. Akad. Nauk SSSR},
   volume={124},
   date={1959},
   pages={282--284},
   %issn={0002-3264},
   %review={\MR{0102055 (21 \#850)}},
}

%\bib{weinstein-Fixed-pnt}{article}{
   %author={Weinstein, Alan},
   %title={A fixed point theorem for positively curved manifolds},
   %journal={J. Math. Mech.},
   %volume={18},
   %date={1968/1969},
   %pages={149--153},
   %review={\MR{0227894 (37 \#3478)}},
%}

\bib{vaisala}{article}{
   author={V{\"a}is{\"a}l{\"a}, Jussi},
   title={A proof of the Mazur--Ulam theorem},
   journal={Amer. Math. Monthly},
   volume={110},
   date={2003},
   number={7},
   pages={633--635},
   %issn={0002-9890},
   %review={\MR{2001155 (2004d:46021)}},
   %doi={10.2307/3647749},
}

\bib{valentine}{article}{
   author={Valentine, F. A.},
   title={On the extension of a vector function so as to preserve a
   Lipschitz condition},
   journal={Bull. Amer. Math. Soc.},
   volume={49},
   date={1943},
   %pages={100--108},
   %issn={0002-9904},
   %review={\MR{0008251 (4,269d)}},
}

\bib{vinberg-strong}{article}{
   author={Vinberg, {\`E}. B.},
   title={The nonexistence of crystallographic reflection groups in
   Lobachevski\u\i\ spaces of large dimension},
   %language={Russian},
   journal={Funktsional. Anal. i Prilozhen.},
   volume={15},
   date={1981},
   number={2},
   pages={67--68},
   %issn={0374-1990},
   %review={\MR{617472 (83d:51026)}},
}

\bib{vinberg}{article}{
   author={Vinberg, {\`E}. B.},
   title={Discrete groups of reflections in Lobachevski\u\i\ spaces of large
   dimensions},
   %language={Russian},
   note={Modules and algebraic groups, 2},
   journal={Zap. Nauchn. Sem. Leningrad. Otdel. Mat. Inst. Steklov. (LOMI)},
   volume={132},
   date={1983},
   pages={62--68},
   %issn={0373-2703},
   %review={\MR{717573 (85c:51028)}},
}

\bib{walsh}{thesis}{
author={Genevieve Walsh},
title={Great circle links in the three-sphere},
journal={\tt arXiv:math/0308048 [math.GT]},
date={2003},
type={Ph.D. thesis}
}

\bib{weyl}{article}{
author={H. Weyl}, 
title={On the volume of tubes}, 
journal={Amer. J. Math.},
volume={61},
date={1939}, 
pages={461--472},
}

\bib{weinstein}{article}{
   author={Weinstein, Alan},
   title={Positively curved $n$-manifolds in $\RR^{n+2}$},
   journal={J. Differential Geometry},
   volume={4},
   date={1970},
   pages={1--4},
   %issn={0022-040X},
   %review={\MR{0264562 (41 \#9154)}},
}

\bib{white}{article}{
   author={White, Brian},
   title={Infima of energy functionals in homotopy classes of mappings},
   journal={J. Differential Geom.},
   volume={23},
   date={1986},
   number={2},
   pages={127--142},
   issn={0022-040X},
   review={\MR{845702 (87m:58039)}},
}

%\bib{whitehead}{article}{
%    Author = {Whitehead, J.H.C.},
%    Title = {Certain theorems about three-dimensional manifolds. I.},
%    Journal = {The Quarterly Journal of Mathematics. Oxford Series},
    %Journal = {{Q. J. Math., Oxf. Ser.}},
    %ISSN = {0033-5606},
%    Volume = {5},
 %   Pages = {308--320},
%    Year = {1934},
%    Publisher = {Oxford University Press, Oxford},
    %Language = {English},
    %Zbl = {0010.27504}
%}

\bib{wilking-2000}{article}{
   author={Wilking, Burkhard},
   title={On fundamental groups of manifolds of nonnegative curvature},
   journal={Differential Geom. Appl.},
   volume={13},
   date={2000},
   number={2},
   pages={129--165},
   %issn={0926-2245},
   %review={\MR{1783960 (2001g:53076)}},
   %doi={10.1016/S0926-2245(00)00030-9},
}

\bib{wilking-2003}{article}{
   author={Wilking, Burkhard},
   title={Torus actions on manifolds of positive sectional curvature},
   journal={Acta Math.},
   volume={191},
   date={2003},
   number={2},
   pages={259--297},
   %issn={0001-5962},
   %review={\MR{2051400 (2005g:53063)}},
   %doi={10.1007/BF02392966},
}

\bib{wilton}{webpage}
{author={Henry Wilton},
title={In Memoriam J. R. Stallings --- Topology of Finite Graphs},
date={2008},
url={https://ldtopology.wordpress.com/2008/12/01/}
}

\bib{zalgaller-shperical-polygon}{article}{
   author={Zalgaller, V. A.},
   title={On deformations of a polygon on a sphere},
   %language={Russian},
   journal={Uspehi Mat. Nauk (N.S.)},
   volume={11},
   date={1956},
   number={5(71)},
   pages={177--178},
   %issn={0042-1316},
   %review={\MR{0083768 (18,758e)}},
}

\bib{zalgaller-polyhedra}{article}{
   author={Zalgaller, V. A.},
   title={Isometric imbedding of polyhedra},
   %language={Russian},
   journal={Dokl. Akad. Nauk SSSR},
   volume={123},
   date={1958},
   pages={599--601},
   %issn={0002-3264},
   %review={\MR{0103511 (21 \#2279)}},
}

\bib{zamfirescu}{article}{
   author={Zamfirescu, Tudor},
   title={Baire categories in convexity},
   journal={Atti Sem. Mat. Fis. Univ. Modena},
   volume={39},
   date={1991},
   number={1},
   pages={139--164},
   %issn={0041-8986},
   %review={\MR{1111764 (92c:52002)}},
}

\bib{yau}{article}{
   author={Yau, Shing Tung},
title={Non-existence of continuous convex functions on certain Riemannian manifolds},
   journal={Math. Ann.},
   volume={207},
   date={1974},
   pages={269--270},
   %issn={0025-5831},
   %review={\MR{0339008 (49 \#3771)}},
}

\bib{yau-ricci}{article}{
   author={Yau, Shing Tung},
   title={Some function-theoretic properties of complete Riemannian manifold and their applications to geometry},
   journal={Indiana Univ. Math. J.},
   volume={25},
   date={1976},
   number={7},
   pages={659--670},
   %issn={0022-2518},
   %review={\MR{0417452 (54 \#5502)}},
}

\bib{yoneyama}{article}{
author={Yoneyama, Kuniz\^{o}},
title={Theory of Continuous Set of Points},
journal={Tohoku Mathematical Journal, First Series},
volume={12},
date={1917},
pages={43--158}
}


\end{biblist}
\end{bibdiv}