\RequirePackage{snapshot}
\documentclass[twoside]{book}

\usepackage{problems}
\usepackage[colorlinks=true,
citecolor=black,
linkcolor=black,
anchorcolor=black,
filecolor=black,
menucolor=black,
urlcolor=black,
pdftitle={Puzzles in geometry that I know and love},
pdfsubject={Geometry},
pdfauthor={Anton Petrunin}
]{hyperref}
\makeindex

\begin{document}


\title{Puzzles in geometry \\
that I know \\ and love}
\author{Anton Petrunin}
\date{}
\maketitle

\null\vfill\noindent{\begin{lpic}[t(-0 mm),b(-0 mm),r(0 mm),l(0 mm)]{pics/by-sa(0.5)}\end{lpic} This work is licensed under the Creative Commons Attribution-ShareAlike 4.0 International License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/4.0/.}

\ 

\thispagestyle{empty}
\noindent{\tt
%http://www.createspace.com/5230762 
%\\
arXiv:0906.0290 [math.HO]
%\\
%\\
%ISBN-13: 978-1506028590
%\\
%ISBN-10: 1506028594 
}
\thispagestyle{empty}
\tableofcontents
\thispagestyle{empty}

\newpage
\thispagestyle{empty}
\section*{Preface}

This collection is about ideas, and it is not about theory.
An idea might feel more comfortable in a suitable theory,
but it has its own live and history, and it can speak for itself --- I hope you will hear it.

I am collecting these problems for fun, 
but they might be used to improve 
the problem solving skills in geometry.
Every problem has a short elegant solution ---
this gives a hint which was not available
when the problem was discovered.

\parbf{How to read it.}
Open at a random chapter, make sure you like the practice problem --- if yes try to solve a random problem in the chapter.
A semisolution is given in the end of the chapter,
but think before reading,
otherwise it might not help. 

\parbf{Acknowledgments.} 
I want to thank everyone who helped me;
here is an incomplete list:
Stephanie Alexander,
Miroslav Ba\v{c}\'{a}k, 
Christopher Croke,
Bogdan Georgiev,
Sergei Gelfand,
Jouni Luukkainen,
Alexander Lytchak,
Rostislav Matveyev, 
Peter Petersen, 
Idzhad Sabitov,
Serge Tabachnikov,
Sergio Zamora Barrera.

This collection is partly inspired by connoisseur's collection of puzzles  by Peter Winkler \cite[][]{winkler}.
Number of problems were suggested on MathOverflow \cite[][]{One-step}.

\vfill

Some problems are marked by $\circ$, $*$, $+$ or $\sharp$.
\begin{itemize}
\item[$\circ$] --- easy problem;%\easy
\item[$*$] --- the solution requires at least two ideas;%\hard
\item[$+$] --- the solution requires knowledge of a theorem;%\thm
\item[$\sharp$] --- there are interesting solutions based on different ideas.%\many
\end{itemize}


\include{curves}
\include{surfaces}
\include{comparison}
\include{curvature-free}
\include{metric}
\include{actions}
\include{topology}
\include{poly}
\include{descrete}
%\include{unfinished}
%\include{open}

%the total number of problems is \thethm.

\backmatter
\newpage
\phantomsection
{\scriptsize
\input{problems.ind}
}
\sloppy
\printbibliography[heading=bibintoc]
\fussy


\end{document}
