\csname @openrightfalse\endcsname
\chapter{Unfinished problems}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Thin lens}
\label{Thin lens}

Recall that Gauss curvature of a surface is defined as product of its principle curvatures.

If the surface lies in the Euclidean space then Gauss curvature equals to the intrinsic curvature of the surface. 
For general Riemannian manifold, Gauss curvature is the difference between intrinsic curvature of the surface and the sectional curvature of ambient space in the direction of the tangent plane.

\begin{pr}
Let $M$ be positively curved 3-dimensional manifold
and $L\subset M$ is a thin lens; that is, $L$ is convex set bounded by two smooth discs that meet at their common boundary at a small angle.
Show that the integral of Gauss curvature along each disc is small. 
\end{pr}

Note that the intrinsic curvature of the disc might be essentially bigger than zero; an example can be constructed in $M=\mathbb{S}^2\times \RR$






%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\parbf{Thin lens.}
Assume that the lens $L$ is bounded by two discs $\Delta$ and $D$.
Let $f=\dist_{\Delta}|_D$; that is, $f$ is the restriction of the distance function $\dist_{\Delta}$ to $\Delta$.

Assume $f$ is smooth.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Sphere with singularities}
\label{Sphere with singular points}

\begin{pr}
Let $\Sigma$ be spherical polyhedral space homeomorphic to the 2-sphere
and $\omega_1,\dots,\omega_n$ be the curvatures its singular points.
Set
\[\delta_i=\min\set{|\tfrac{\omega_i}2-2\cdot k\cdot\pi|}{k\in\ZZ}.\]
Show that in the unit sphere there is a closed polygonal curve with sides 
$\delta_1,\dots,\delta_n$.  
\end{pr}

\parit{Semisolution.}
Fix a regular point $p\in\Sigma$;
let $\gamma$ be a loop at $p$ that does not pass thru the singularities of $\Sigma$.
The $h_\gamma$ ...

Note that for the constant loop $h_\gamma=1$.
If $\gamma$ goes around a single singular point with curvature $\omega_i$,
then $|h_\gamma-1|_{SU(2)}=\delta_i$.

